---
title: "Practical Machine Learning Course"
author: "Andres Lopez"
date: "September 2nd, 2019"
output: html_document
---

# 1. Introduction
This is a notebook for the project included in the course "Practical Machine Learning".  We have several data inputs from *health devices*, collecting data from accelerometers on the belt, forearm, arm, and dumbell from several users.

I am going to do an exploratory analysis of the input data from the accelerometers, trying to detect the relationships between them.  After this, I am going to decide the best prediction model and implement it.

# 2. Load the libraries for the exploratory analysis

```{r}
library(caret)
library(ggplot2)
library(forecast)
library(randomForest)
library(readr)
library(ISLR)
```

# 3. Load data
The fist step is load the training data, used for creating our model, and the testing data, used to test our model after its creation.

```{r}
pml_training <- read_csv("pml-training.csv")
pml_testing <- read_csv("pml-testing.csv")
```

# 4. First view of the data
After a first view of the training data, there are a lot of columns with *NA* value on a lot of the data records.  I will create a subset of the data removing these columns from the training data, to keep the relevant data for the prediction model.

```{r}
training <- subset(pml_training,select = c(X1,user_name,cvtd_timestamp,gyros_belt_x,gyros_belt_y,gyros_belt_z,accel_belt_x,accel_belt_y,accel_belt_z,magnet_belt_x,magnet_belt_y,magnet_belt_z))
View(training)

```


# 5. Finding correlations between data






